draft

### 2021-05-13 code/draft.Rmd
responder test

source("~/Dropbox/42-JCHWANG-RUTGERS/Projects-Rutgers/Src/utils.R")

@@

## Body weight
### Overall, plotting all data
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210224-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

@@

>>>>

source("code/utils.R")

@@

## Body weight
### Overall, plotting all data
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210402-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

@@

```{r}
n_sd = 1.5

BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_g, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";")

BW_f_3 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_g > vf_ul, "Overweight", ifelse(Weight_g < vf_ll, "Underweight", "Normal")))

ggplot(BW_f_3, aes(x = TimePoint_Weeks, y = Weight_g)) +
    geom_point(size = 1.5, aes(color = Flag)) +
    geom_line(aes(group = MouseID, color = Flag)) +
    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.3) +
    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 1) +
    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
    facet_grid(Sex ~ BirthMode) +
    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
    scale_x_continuous(breaks = seq(4, 15, 2)) +
    labs(x = "Weeks", y = "Body Weight (g)")

BW_f_3 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% mutate(OR_over = N_over/(N_sub-N_over)/(N_over[1]/(N_sub[1]-N_over[1])))
```

```{r}
n_sd = 1.5

BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_gain, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";", convert = T)

BW_f_4 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% ungroup %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_gain > vf_ul, "Overweight", ifelse(Weight_gain < vf_ll, "Underweight", "Normal")))

ggplot(BW_f_4, aes(x = TimePoint_Weeks, y = Weight_gain)) +
    geom_point(size = 1.5, aes(color = Flag)) +
    geom_line(aes(group = MouseID, color = Flag)) +
    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.3) +
    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 1) +
    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
    facet_grid(Sex ~ BirthMode) +
    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
    scale_x_continuous(breaks = seq(4, 15, 2)) +
    labs(x = "Weeks", y = "Body Weight gain(% to week 3 body weight)")

BW_f_4 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% mutate(OR_over = N_over/(N_sub-N_over)/(N_over[1]/(N_sub[1]-N_over[1])))
```
